A fully labelled proof system for intuitionistic modal logics

### 2019-10-08 caleidoscope/conclusion.tex
small modif

For a restricted class of logics defined by so-called \emph{path axioms}: $(\DIA^k\BOX A \IMP\BOX^m A) \AND (\DIA^k A \IMP \BOX^m\DIA A)$ the standard labelled framework with one relation $R$ was enough for Simpson to get a strong connection between the sequent system, the axiomatisation and the birelational semantics~\ref{simpson:phd}.
%
%\todo{For path axioms we must have that adding the rule for the two sides of the axiom is equivalent to adding the rule that doesn't make use of the pre-order. Is it possible to see that directly on the proof theoretical side?}
%\sonia{probably not because the preorder is introduced/used in other rules for $\BOX$ and $\IMP$}
%
We believe that the framework presented here might be the more appropriate way to treat logics outside of the path axioms definable fragment.

>>>>

For a restricted class of logics defined by so-called \emph{path axioms}: $\fm{(\DIA^k\BOX A \IMP\BOX^m A) \AND (\DIA^k A \IMP \BOX^m\DIA A)}$ the standard labelled framework with one relation $R$ was enough for Simpson to get a strong connection between the sequent system, the axiomatisation and the birelational semantics~\ref{simpson:phd}.
%
%\todo{For path axioms we must have that adding the rule for the two sides of the axiom is equivalent to adding the rule that doesn't make use of the pre-order. Is it possible to see that directly on the proof theoretical side?}
%\sonia{probably not because the preorder is introduced/used in other rules for $\BOX$ and $\IMP$}
%
We believe that the framework presented here might be the more appropriate way to treat logics outside of the path axioms definable fragment.
